Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-05-16 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
updating pdf

	\par \citet{cargill_implications_1994,cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component, the so-called ``smoking gun'' of nanoflare heating. Though many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} have made a positive detection of nanoflare heating difficult. However, \citet{brosius_pervasive_2014}, using obsservations from the \textit{EUNIS-13} sounding rocket, identified relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.

@@

	\par A similar scaling has been claimed for hot emission such that $\mathrm{EM}\propto T^{-b}$. Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim\log{T}\lesssim7.2$. However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012}, find $7\lesssim b\lesssim10$, with uncertainties of $\pm2.5-3$, for 15 AR cores thoguh \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.

>>>>

	\par \citet{cargill_implications_1994,cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component, the so-called ``smoking gun'' of nanoflare heating. Though many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} have made a positive detection of nanoflare heating difficult. However, \citet{brosius_pervasive_2014}, using observations from the \textit{EUNIS-13} sounding rocket, identified relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.

@@

	\par A similar scaling has been claimed for hot emission such that $\mathrm{EM}\propto T^{-b}$. Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim T\lesssim10^{7.2}$. However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012}, find $7\lesssim b\lesssim10$, with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.
